Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Collaped gender plots to 3 levels instead of 4

GLAD.prepan %>%
  ggplot(aes(x = Gender)) +
  geom_bar(fill = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants")

@@

GLAD.retro %>%
  ggplot(aes(x = Gender)) +
  geom_bar(fill = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the GLAD/EDGI retro cohort",
       subtitle = paste("N =", dim(GLAD.retro)[1]),
       x = "",
       y = "N participants")

@@

NBR.retro %>%
  ggplot(aes(x = Gender)) +
  geom_bar(fill = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the NBR retro cohort",
       subtitle = paste("N =", dim(NBR.retro)[1]),
       x = "",
       y = "N participants")

@@

RAMP.retro %>%
  ggplot(aes(x = Gender)) +
  geom_bar(fill = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the RAMP retro cohort",
       subtitle = paste("N =", dim(RAMP.retro)[1]),
       x = "",
       y = "N participants")

@@

dat.retro %>% 
  ggplot(aes(x = Gender, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the retro cohorts",
       x = "",
       y = "") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

>>>>

GLAD.prepan %>%
  ggplot(aes(x = Gender_collapsed)) +
  geom_bar(fill = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants")

@@

GLAD.retro %>%
  ggplot(aes(x = Gender_collapsed)) +
  geom_bar(fill = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the GLAD/EDGI retro cohort",
       subtitle = paste("N =", dim(GLAD.retro)[1]),
       x = "",
       y = "N participants")

@@

NBR.retro %>%
  ggplot(aes(x = Gender_collapsed)) +
  geom_bar(fill = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the NBR retro cohort",
       subtitle = paste("N =", dim(NBR.retro)[1]),
       x = "",
       y = "N participants")

@@

RAMP.retro %>%
  ggplot(aes(x = Gender_collapsed)) +
  geom_bar(fill = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the RAMP retro cohort",
       subtitle = paste("N =", dim(RAMP.retro)[1]),
       x = "",
       y = "N participants")

@@

dat.retro %>% 
  ggplot(aes(x = Gender_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the retro cohorts",
       x = "",
       y = "") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())
